---
title: "Notebook 4: Modelling fitting and predicting"
output: html_notebook
---

Model: Linear regression model: Predicting the amount of tips given predictors
```{r}
setwd(getwd())
train_set = read.csv("../preprocessed_data/train_set.csv")
test_set =read.csv("../preprocessed_data/test_set.csv")
```

Check distribution of response variable
Even though a bit positively skewed, we still 
assume it follows a normal distribution
```{r}
hist(train_set$tip_amount,xlab = "tip",ylab = "density",main = "Tip distribution")
```
Fitting interaction model and non-interaction model
```{r}
train_set$weekday = factor(train_set$weekday)
train_set$weather = factor(train_set$weather)
train_set$peak_time = factor(train_set$peak_time)

# Model without interaction
no_inter_model = lm(tip_amount ~ weekday+weather+peak_time+trip_distance,data = train_set)
summary(no_inter_model)

# Model with interaction
inter_model = lm(tip_amount ~ (weekday+weather+peak_time+trip_distance)^2,data = train_set)
summary(inter_model)
```

Test if interaction effect is 0, p-value is less than 0.05, we reject H0 that interaction
effect is 0.
```{r}
anova(no_inter_model,inter_model)
```

Use step-wise selection to select the best model with BIC criterion
 step wise selection delete no variable in both cases
```{r}
step_model = step(inter_model,k=log(length(train_set)))
summary(step_model)

step_no_model = step(no_inter_model,k = log(length(train_set)))
summary(step_no_model)
```

Comparison between 2 models
NO interaction model
```{r}
test_set$weekday = factor(test_set$weekday)
test_set$weather = factor(test_set$weather)
test_set$peak_time = factor(test_set$peak_time)
prediction = predict(no_inter_model,data.frame(test_set[c("weekday","weather","peak_time","trip_distance")]))
```


Evaluation metric of of non-interaction model
```{r}
# r2
summary(no_inter_model)$r.squared

## Mean squared error
mean((prediction-test_set$tip_amount)^2)

##  Mean absolute  error
mean(abs(prediction-test_set$tip_amount))

```


Evaluation metric of of interaction model
```{r}
prediction = predict(inter_model,data.frame(test_set[c("weekday","weather","peak_time","trip_distance")]))

# r2
summary(inter_model)$r.squared

## Mean squared error
mean((prediction-test_set$tip_amount)^2)

##  Mean absolute  error
mean(abs(prediction-test_set$tip_amount))

```


Diagnostic plot for the final model
```{r}
plot(inter_model)
```

